\documentclass{article}
\usepackage[english]{babel}

\renewcommand{\topfraction}{1}
\begin{document}

\section{Using Footnotes in Figure Captions - Demo}

In general, foonotes should not be used in TeX Boxes, especially
figures or even figure captions. For figures themselves, the
{\tt minipage} environment provides an option. If you insist on
having a footnote in the caption of a figure, this hack might help.
But beware! You must find the right location for the \verb?\footnotetext?
command in your document, and there is a certain chance that such a place
will not exist. This document is a perfect example. The figure and its footnote
are on different pages. I consider myself a very tenacious \LaTeX hacker,
and I gave up.

\hfill -- Ulrich Germann
\begin{itemize}
\item use \verb?\addtocounter{footnote}{1}\footnotetext{? {\itshape [the footnote]}\verb?}?
      in the regular, running text to create a footnote.
\item put a label in that footnote
\item references that label in superscript wherever you want
\end{itemize}

\begin{figure}[b]
\small
\begin{minipage}{5.5in}
The footnote for this sentence will show up within the 
figure\footnote{See? Right here!}.

\begin{verbatim}
\begin{document} 
[Main text was here.] 
\begin{figure} 
\small 
\begin{minipage}{5.5in] 
The footnote for this sentence will show up within the 
figure\\footnote{See? Right here!}. 
{\tt ... [this is where the code was]} 
\end{minipage} 
\caption{How to put a footnote in a figure caption$^{\ref{FootNoteForFigureCaption}}$.} 
\label{sample code}
\end{figure}

\addtocounter{footnote}{1}\footnotetext{This is the footnote for the
figure caption\label{FootNoteForFigureCaption}}

\noindent
Sample code is given in figure \ref{sample code}.

\noindent
Here is a nother footnote \footnote{My second footnote.}.
\end{document}
\end{verbatim} 

\end{minipage}
\caption{How to put a footnote in a figure caption$^{\ref{FootNoteForFigureCaption}}$.}
\label{sample code}
\end{figure}

\addtocounter{footnote}{1}\footnotetext{This is the footnote for the
figure caption\label{FootNoteForFigureCaption}}

\noindent
Sample code is given in figure \ref{sample code}.

\noindent
Here is a nother footnote \footnote{My second footnote.}.

\end{document}

